Evaluation of the article

### 2024-09-03 pages/paper_evaluation.qmd
docs(evaluation): add key for symbols
fix(eval): correction to Anagnostou ISPOR 4 and 5

@@

| **4 Is the time horizon given?**<br>...the time period covered by the simulation was reported. | ✅ | ✅ | ✅ | ✅ | ✅ | ❌ |
| **5 Are all simulated strategies/scenarios specified?**<br>...the comparators under test were described in terms of their components, corresponding variations, etc | ✅ | ✅ | ✅ | ✅ | ✅ | N/A |

>>>>

In this section and below, the criteria for each study are marked as either being fully met (✅), partially met (🟡), not met (❌) or not applicable (N/A).

@@

| **4 Is the time horizon given?**<br>...the time period covered by the simulation was reported. | ✅ | ✅ | ✅ | ✅ | ❌ |
| **5 Are all simulated strategies/scenarios specified?**<br>...the comparators under test were described in terms of their components, corresponding variations, etc | ✅ | ✅ | ✅ | ✅ | N/A |
